---
title: "Max Greene HW10"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

#6.2.1
In  problem  6.2.1  in  the  textbook,  use  the  given  information  to  compute  the  $(1-\alpha)100\%$ confidence interval.

##a
$H_0 : \mu=120$ versus $H_1 : \mu < 120 ; \bar{y}=114.2,n=25, \sigma =18, \alpha= 0.08$
```{r}
mu <- 120 
y_bar <- 114.2
n <- 25
sigma <- 18
alpha <- 0.08
(z <- (y_bar-mu)/(sigma/sqrt(n)))
(z_alpha_norm <- qnorm(0.08))
(z_alpha_test <- qnorm(0.08))*(sigma/sqrt(n))+mu
```

##b
$H_0 : \mu=42.9$ versus $H_1 : \mu \ne 42.9 ; \bar{y}=45.1,n=16, \sigma =3.2, \alpha= 0.01$

```{r}
mu <- 42.9
y_bar <- 45.1
n <- 16
sigma <- 3.2
alpha <- 0.01
(z <- (y_bar-mu)/(sigma/sqrt(n)))
(z_alpha_norm <- qnorm(c(alpha/2,1-alpha/2)))
(z_alpha_test <- qnorm(c(alpha/2,1-alpha/2)))*(sigma/sqrt(n))+mu
```

##c
$H_0 : \mu=14.2$ versus $H_1 : \mu > 14.2 ; \bar{y}=15.8 , n=9, \sigma = 4.1 , \alpha= 0.13$

```{r}
mu <- 14.2
y_bar <- 15.8
n <- 9
sigma <- 4.1
alpha <- 0.13
(z <- (y_bar-mu)/(sigma/sqrt(n)))
(z_alpha_norm <- qnorm(1-alpha))
(z_alpha_test <- qnorm(1-alpha))*(sigma/sqrt(n))+mu
```

#6.2.2
Random sample, 22 diagnosed. 

Past ADD score $\mu_{ADD} = 95, \sigma_{ADD} = 15$.

Use $\alpha = 0.06$. For what values of $\bar{y}$ should $H_0$ be rejected if $H_1$ is two-sided?

```{r}
mu <- 95
sigma <- 15
n <- 22
alpha <- 0.06
(z_alpha_norm <- qnorm(c(alpha/2,1-alpha/2)))
(z_alpha_test <- qnorm(c(alpha/2,1-alpha/2)))*(sigma/sqrt(n))+mu
```

#6.2.4
Population mean 32,500.
15 sample drivers 33,800 on new tires. Assume $\sigma=4000$ for both cases.
Can the company claim a statisticaly significant difference at $\alpha=0.05$?

```{r}
mu <- 32500
sigma <- 4000
n <- 15
alpha <- 0.05
(z_alpha_norm <- qnorm(1-alpha))
mu
(z_alpha_test <- qnorm(1-alpha))*(sigma/sqrt(n))+mu
```

#6.2.10
Average blood pressure $\mu = 120, \sigma = 12$.
Sample of $n=50$ women, $\mu = 125.2$.

$H_0:\mu_{exam}\neq\mu_{norm}$ , $H_1:\mu_{exam}=\mu_{norm}$

```{r}
mu <- 120
sigma <- 12
n <- 50
alpha <- 0.05
(z_alpha_norm <- qnorm(1-alpha))
(z_alpha_test <- qnorm(1-alpha))*(sigma/sqrt(n))+mu

alpha <- 0.01
(z_alpha_norm <- qnorm(1-alpha))
(z_alpha_test <- qnorm(1-alpha))*(sigma/sqrt(n))+mu
```

This data shows a significant increase in heartrate with 99% confidence.

#6.3.2
$67$\% A/J are right-pawed.  
Same protocol on $n=35$ mice of strain A/HeJ, $18/35$ right-pawed.
Test if A/HeJ mice were significantly different than A/J strains. Use $\alpha = 0.05$.

First check the inequality
$$
0 < np_0-3\sqrt{np_0(1-p_0)}<np_0+3\sqrt{np_0(1-p_0)}<n
$$

```{r}
n <- 35
p_0 <- .67
0
n*p_0-3*sqrt(n*p_0*(1-p_0))
n*p_0+3*sqrt(n*p_0*(1-p_0))
n
```

```{r}
n <- 35
k <- 18
p_0 <- .67
alpha <- 0.05
(z <- (k-n*p_0)/(sqrt(n*p_0*(1-p_0))))
(z_alpha <- qnorm(c(alpha/2,1-alpha/2)))
```

#6.3.4

Suppose $H_0:p=0.45$ is to be tested against $H_1:p>0.45$ at $\alpha=0.14$ level where $p=P(i \text{th trial ends in success})$ If sample size is $n=200$ what is smallest number of successes that will cause $H_0$ to be rejected?

```{r}
n <- 200
k <- c(79,80)
p_0 <- .45
alpha <- 0.14
(z <- (k-n*p_0)/(sqrt(n*p_0*(1-p_0))))
(z_alpha <- qnorm(c(alpha/2,1-alpha/2)))
```

#6.4.2

Carry out the details to verify the decision rule
change cited on p. 364 in connection with Figure 6.4.6

???

#6.4.6

$n=36, \sigma = 8$ for testing $H_0 : \mu = 60$ versus $H_1 : \mu \neq 60$ at $\alpha=0.07$.  
Intends to reject $H_0$ if $\bar{y}$ falls in critical region region $(60-\bar{y}^*,6-+\bar{y}^*)$

(a) Find $\bar{y}^*$

```{r}
mu <- 60
n <- 36
sigma <- 8
alpha <- 0.07
(z_alpha_norm <- qnorm(c(alpha/2,1-alpha/2)))
(z_alpha_test <- qnorm(c(alpha/2,1-alpha/2)))*(sigma/sqrt(n))
```

(b) Power of test when $\mu=62$, true mean $u_t=60$?  
First calculate $\beta$.
```{r}
mu <- 62
muTrue <- 60
n <- 36
sigma <- 8
alpha <- 0.07
(Z_alpha <- (mu-muTrue)/(sigma/sqrt(n)))
(beta <- pnorm(Z_alpha))
(power <- 1-beta)
```

(c) Power of test when $\mu=62$ if critical region defined correctly?

???

#6.4.8
Will $n=45$ be a sufficiently large sample to test $H_0: \mu = 10$ versus $H_1 : \mu \neq 10$ at $\alpha=0.05$ if experimenter
wants $\beta < 0.20$ when $\mu = 12$? Assume $\sigma=4$. 

Using the guidelines from Ex. 6.4.1:
$$
P(|Z| \geq 1.64)=0.05 \Rightarrow P(Z \geq 1.64)=0.025 \\
\bar{y}^*=10+1.64\frac{4}{\sqrt{n}}
$$
Then, using power equation,
$$
1-\beta = P(\text{reject }H_0 | H_1 \text{true})=P(\bar{Y}\geq \bar{y}^*|\mu=12)=0.80
$$
Now, find associated $Z_\alpha$
```{r}
beta <- 0.20
qnorm(beta)
```
So,
$$
\begin{aligned}
\bar{y}^*&=12-0.84\frac{4}{\sqrt{n}}\\
10+1.64\frac{4}{\sqrt{n}}&=12-0.84\frac{4}{\sqrt{n}} \\
(1.64+0.84)\frac{4}{\sqrt{n}}&=2\\
n&=\Big(\frac{4*2.48}{2}\Big)^2 \approx 24.6
\end{aligned}
$$

Yes, a sample of $n=40$ will be large enough to guarantee a power of $0.80$.

#6.4.12
Urn contains $n=10$ chips with $w=$ no. white and $n-w=$ no. red.  
$H_0:$ exactly half chips red, $H_1:$ more than half red.
Draw $3$ chips and reject $H_0$ if two or more white. Find $\alpha$. Then find $\beta$ when urn is $60%$ white and $70%$ white.

$$
\alpha=P(\bar{Y} > \bar{y}^* | H_0 \text{ true})
$$

Therefore, $\alpha$ will be the probability that there are actually 5 white in total given either 2 or 3 out of the initial 3 being white. So, this probability is the sum of the probabilities of 2 and 3 out of the remaining 7 chips being white.

```{r}
(alpha <- sum(dbinom(c(2,3),7,prob=.5)))
(beta60 <- 1-sum(dbinom(c(2,3),7,prob=.6)))
(beta70 <- 1-sum(dbinom(c(2,3),7,prob=.7)))
```

#6.4.14
Sample size $n=1$ taken from pdf $f_Y(y)=(\theta+1)y^\theta, 0 \leq y \leq 1$.
Reject $H_0: \theta=1$ for $H_1:\theta > 1$ if $y \geq 0.90$. What is test's level of significance?





