---
title: "Max Greene HW10"
output: pdf_document
---

#6.2.1
In  problem  6.2.1  in  the  textbook,  use  the  given  information  to  compute  the  $(1-\alpha)100\%$ confidence interval.
##a
$H_0 : \mu=120$ versus $H_1 : \mu < 120 ; \bar{y}=114.2,n=25, \sigma =18, \alpha= 0.08$
```{r}
mu <- 120 
y_bar <- 114.2
n <- 25
sigma <- 18
alpha <- 0.08
(z <- (y_bar-mu)/(sigma/sqrt(n)))
(z_alpha_norm <- qnorm(0.08))
(z_alpha_test <- qnorm(0.08))*(sigma/sqrt(n))+mu
```

##b
$H_0 : \mu=42.9$ versus $H_1 : \mu \ne 42.9 ; \bar{y}=45.1,n=16, \sigma =3.2, \alpha= 0.01$

```{r}
mu <- 42.9
y_bar <- 45.1
n <- 16
sigma <- 3.2
alpha <- 0.01
(z <- (y_bar-mu)/(sigma/sqrt(n)))
(z_alpha_norm <- qnorm(c(alpha/2,1-alpha/2)))
(z_alpha_test <- qnorm(c(alpha/2,1-alpha/2)))*(sigma/sqrt(n))+mu
```

##c
$H_0 : \mu=14.2$ versus $H_1 : \mu > 14.2 ; \bar{y}=15.8 , n=9, \sigma = 4.1 , \alpha= 0.13$

```{r}
mu <- 14.2
y_bar <- 15.8
n <- 9
sigma <- 4.1
alpha <- 0.13
(z <- (y_bar-mu)/(sigma/sqrt(n)))
(z_alpha_norm <- qnorm(1-alpha))
(z_alpha_test <- qnorm(1-alpha))*(sigma/sqrt(n))+mu
```

#6.2.2
Random sample, 22 diagnosed. 

Past ADD score $\mu_{ADD} = 95, \sigma_{ADD} = 15$.

Use $\alpha = 0.06$. For what values of $\bar{y}$ should $H_0$ be rejected if $H_1$ is two-sided?

```{r}
mu <- 95
sigma <- 15
n <- 22
alpha <- 0.06
(z_alpha_norm <- qnorm(c(alpha/2,1-alpha/2)))
(z_alpha_test <- qnorm(c(alpha/2,1-alpha/2)))*(sigma/sqrt(n))+mu
```

#6.2.3

#6.2.4
Population mean 32,500.
15 sample drivers 33,800 on new tires. Assume $\sigma=4000$ for both cases.
Can the company claim a statisticaly significant difference at $\alpha=0.05$?

```{r}
mu <- 32500
sigma <- 4000
n <- 15
alpha <- 0.05
(z_alpha_norm <- qnorm(1-alpha))
mu
(z_alpha_test <- qnorm(1-alpha))*(sigma/sqrt(n))+mu
```

#6.2.9

#6.2.10
Average blood pressure $\mu = 120, \sigma = 12$.
Sample of $n=50$ women, $\mu = 125.2$.

$H_0:\mu_{exam}\neq\mu_{norm}$ , $H_1:\mu_{exam}=\mu_{norm}$

```{r}
mu <- 120
sigma <- 12
n <- 50
alpha <- 0.05
(z_alpha_norm <- qnorm(1-alpha))
(z_alpha_test <- qnorm(1-alpha))*(sigma/sqrt(n))+mu

alpha <- 0.01
(z_alpha_norm <- qnorm(1-alpha))
(z_alpha_test <- qnorm(1-alpha))*(sigma/sqrt(n))+mu
```

This data shows a significant increase in heartrate with 99% confidence.

#6.3.1

#6.3.2

#6.3.4

#6.3.7

#6.3.9

#6.4.2

#6.4.3

#6.4.6

#6.4.8

#6.4.12

#6.4.13

#6.4.14



