---
title: "Prob & Stat HW4"
output: pdf_document
author: "Maxwell Greene"
---

```{r,include=FALSE,message=FALSE}
library(tidyverse)
library(VGAM)
```

#Question #7
Rayleigh Distribution:
$$
f(x)=\frac{x}{a^2}e^{\frac{x^2}{2a^2}}, 
\hspace{5mm} \text{where} \hspace{5mm}a>0,0\leq x<\infty
$$

##(a)
$$
\int_{0}^{\infty} f(x)dx=
\int_{0}^{\infty} \frac{x}{a^2}e^{-\frac{x^2}{2a^2}}dx
$$
Performing the u-substitution $u=\frac{x^2}{2a^2}$, $du=\frac{x}{a^2}dx$ gives
$$
\begin{aligned}
\int_{0}^{\infty} f(x)dx
&=\int_{0}^{\infty} e^{-u} du \\
&=-e^{-u}\big|^{\infty}_{0} = -e^{-\frac{x^2}{2a^2}}\big|_{0}^{\infty}
=-e^{-\infty}+e^{0}=\boxed{1}
\end{aligned}
$$

###(d)
```{r,warning=FALSE,fig.width=4,fig.height=3}
x<-seq(0,2,.01)
y1<-drayleigh(x,scale=.1)
y2<-drayleigh(x,scale=.5)
y3<-drayleigh(x,scale=1)
data<-data.frame(x=rep(x,3),
  alpha=rep(c(1,2,3),3,each=length(x)),
  y1=y1,y2=y2,y3=y3)
ggplot(data) + 
  geom_line(mapping=aes(x=x,y=y1))+
  geom_line(mapping=aes(x=x,y=y2))+
  geom_line(mapping=aes(x=x,y=y3))
```

#Question #8
Expectation of Rayleigh Distribution given by
$$
E(R)=
\int_{0}^{\infty} (x * f_{R}) dx=
\int_{0}^{\infty} x \frac{x}{a^2}e^{\frac{x^2}{2a^2}}dx
$$

With $\sigma = 1$ the expected value is
```{r,warning=FALSE}
a<-1
rayleighExpect <- function(x)
{return(x*drayleigh(x,scale=a))}
integrate(rayleighExpect,lower=0,upper=Inf)$value
```
Notably, this is approximately $\sigma \sqrt{\frac{\pi}{2}}$.
```{r}
a*sqrt(pi/2)
```

#Question #10
Probability mass function of dice roll given by

X      | P(X)
-------|--------
 1     | 1/6
 2     | 1/6
 3     | 1/6
 4     | 1/6
 5     | 1/6
 6     | 1/6

I'll write this in R as
```{r}
diceProb <- data.frame(value=1:6,prob=rep(1/6,6))
```
Now, we calculate the expacted value given by $\mu=\sum xP(x)$
```{r}
diceExpected <- sum(diceProb$value*diceProb$prob)
diceExpected
```

And the variance given by $\sigma = \sum P(x)(x-\mu)^{2}$
```{r}
diceVariance<-sum(diceProb$prob*(diceProb$value-diceExpected)^2)
diceVariance
```

#Question #11
Expected Value:
$$
\begin{aligned}
E(Y)&= \int_{-\infty}^{\infty}f_x(\frac{x-\mu}{\sigma})dx \\
&= \frac{1}{\sigma}\int_{-\infty}^{\infty}x*f_xdx - 
\frac{1}{\sigma}\int_{-\infty}^{\infty}\mu*f_xdx\\
&= \frac{\mu}{\sigma} - \frac{\mu}{\sigma} = \boxed{0}
\end{aligned} 
$$
$$
\text{because} \int_{-\infty}^{\infty}x*f_xdx=\mu 
\hspace{5mm} \text{and} \hspace{5mm}
\int_{-\infty}^{\infty}f_xdx=1
$$

Variance:
$$
\begin{aligned}
Var(Y) &= \int_{-\infty}^{\infty} f*(y-\mu)^2dx \\
&= \frac{1}{\sigma^2} \int f * (x-\mu)^2dx 
- \frac{2 \mu}{\sigma}\int f * (x-\mu)dx 
+ \mu^2 \int f dx  \\
&=\frac{1}{\sigma^2}\int f* x^2 dx 
- 2\mu\int f* x dx 
+ \mu^2\int f dx 
-\frac{2\mu}{\sigma}(0)+\mu^2 \\
&= \frac{\sigma^2}{\sigma^2} 
- 2\mu^2 + \mu^2 + \mu^2 = \boxed{1}
\end{aligned}
$$

#Question 3.5.8, 3.5.14, 3.5.30, 3.6.8 on separate sheet.

