---
title: "Prob & Stat HW8"
output: pdf_document
---

#Question 1
$X$, $Y$ independent random variables with $X$,$Y$ ~ $geom(p)$: $p_X(k)=p_Y(y)=p(1-p)^{k-1}, 0<p<1$

If $W=X+Y$, show $$p_W(w)=(w-1)p^2(1-p)^{w-2}, w \geq 1 $$

Hint: $p_W(w)=\sum_{\text{all }k} p_X(k) p_y(w-k)$  

$$
\begin{aligned}
p_W(w)&=\sum_{\text{all }k} p_X(k) p_y(w-k)\\
&=\sum_{\text{all }k} p(1-p)^{1-k} p(1-p)^{w-k-1}\\
&=\sum_{\text{all }k} p^2(1-p)^{w-2}\\
&=\boxed{(w-1)p^2(1-p)^{w-2}}
\end{aligned}
$$

#Question 2
Use $\Gamma(r)=(r-1)\Gamma(r-1)$ to prove $\Gamma(n)=(n-1)!$ if n is a positive integer. Hint: prove by induction.


  $\Gamma(1) = 1$ and $0! = 1$, which verifies the equation for $n = 1$.
Assuming $\Gamma(k) = (k-1)!$, $\Gamma(k+1)=k\Gamma(k)=k(k-1)!=k!$.


#Question 3
Prove that $\Gamma(\frac{1}{2})=\sqrt{\pi}$  
$$
\begin{aligned}
1&=E(Z^2)\\
&=\frac{\sqrt{2}}{\sqrt{\pi}}\int_{0}^{\infty}z^2e^{\frac{-z^2}{2}}dz\\
&=\frac{\sqrt{2}}{\sqrt{\pi}}\int_{0}^{\infty}\frac{(2u)e^{-u}}{\sqrt{2}\sqrt{u}}du, u=\frac{z^2}{2}\\
&=\frac{2}{\sqrt{\pi}}\int_{0}^{\infty}u^{(\frac{3}{2}-1)}e^{-u}du\\
\sqrt{\pi}&=2\Gamma(\frac{3}{2})\\
\sqrt{\pi}&= 2*\frac{1}{2}\Gamma(\frac{1}{2})\\
&\boxed{\sqrt{\pi}=\Gamma(\frac{1}{2})}
\end{aligned}
$$

#Question 4
```{r}
pnorm(1.33,0,1)-pnorm(-0.44,0,1)
```
```{r}
pnorm(0.94,0,1)
```
```{r}
1-pnorm(-1.48,0,1)
```
```{r}
pnorm(-4.32,0,1)
```

#Question 5
###Part (a)
```{r}
pnorm(2.07,0,1)-pnorm(0,0,1)
```
###Part (b)
```{r}
pnorm(-0.11,0,1)-pnorm(-0.64,0,1)
```
###Part (c)
```{r}
1-pnorm(-1.06,0,1)
```
###Part (d)
```{r}
pnorm(-2.33,0,1)
```
###Part (e)
```{r}
1-pnorm(4.61,0,1)
```
#Question 6
```{r}
qnorm(.75,0,1)-qnorm(.25,0,1)
```

