---
title: "Max Greene HW11"
output: pdf_document
---
```{r,message=FALSE}
library(tidyverse)
```

#7.3.3
Could 65,30,55 come from $N(\mu=50,\sigma=10)$? Answer using $\chi^2$ distribution.  
Hint: Let $z_i=\frac{Y_i-50}{10}$.
$$
U=\Sigma_{i-1}^{\infty}Z_i^2=\Big(\frac{65-50}{10}\Big)^2+\Big(\frac{30-50}{10}\Big)^2+\Big(\frac{55-50}{10}\Big)^2
$$
belongs to $\chi^2$ with 3 df.

```{r}
(U <- ((65-50)/10)^2+((30-50)/10)^2+((55-50)/10)^2)
pchisq(U,df=3)
```

#7.3.4
Use the facts that 
$$
\chi^2_{n-1} = \frac{(n-1)S^2}{\sigma^2}\\
Var(\chi^2_k)=2k
$$ 
is a chi square random variable with $(n-1)$ degrees of freedom to prove that:
$$
Var(S^2)=\frac{2\sigma^4}{n-1}
$$

$$
\begin{aligned}
Var(\chi^2_{n-1}) &= Var\Big(\frac{(n-1)S^2}{\sigma^2}\Big) \\
2(n-1)&=\frac{(n-1)^2}{\sigma^4}Var(S^2)\\
\frac{2(n-1)\sigma^4}{(n-1)^2}&=Var(S^2)\\
Var(S^2)&=\boxed{\frac{2\sigma^4}{(n-1)}}
\end{aligned}
$$

#7.3.6

Use the assymptotic normality of $(Y-n)/\sqrt{2n}$ to approximate the 40th percentile of chi square r.v. with $df=200$.
$$
z=\frac{y-200}{\sqrt{2*300}} \approx Norm(0,1)
$$
```{r}
qchisq(.40,df=200)
```


#7.3.14
Evaluate the following using the Student t distribution:
$$
\int_0^\infty \frac{1}{1+x^2}dx
$$
$$
f_{T_n}(x)=\frac{\Gamma(\frac{n+1}{2})}{\sqrt{(n\pi)}\Gamma(\frac{n}{2})(1+\frac{x^2}{n})^{\frac{n+1}{2}}}\\
1=\int_{-\infty}^\infty f_{T_n}(x)dx=\int_{-\infty}^\infty \frac{\Gamma(\frac{n+1}{2})}{\sqrt{(n\pi)}\Gamma(\frac{n}{2})(1+\frac{x^2}{n})^{\frac{n+1}{2}}}dx\\
$$
Now, using $n=1$,
$$
\begin{aligned}
1&=\int_{-\infty}^\infty \frac{\Gamma(1)}{\sqrt{\pi} \Gamma(\frac{1}{2})(1+x^2)}dx\\
&=\frac{1}{\pi}\int_{-\infty}^\infty \frac{1}{(1+x^2)}dx=\frac{2}{\pi}\int_0^\infty \frac{1}{(1+x^2)}dx=\\
&\therefore \int_0^\infty \frac{1}{(1+x^2)}dx=\boxed{\frac{\pi}{2}}
\end{aligned}
$$

#7.4.2

(a):$P(-x \leq T_{22} \leq x) = 0.98$
```{r}
alpha=1-0.98
qt(c(alpha/2,1-alpha/2),df=22)
```

(b):$P(T_{13} \geq x) = 0.85$
```{r}
alpha=1-0.85
qt(alpha,df=13)
```

(c):$P(T_{26} < x) = 0.95$
```{r}
alpha=1-0.95
qt(alpha,df=26)
```

(d):$P(T_{2} \geq x) = 0.025$
```{r}
alpha=1-0.025
qt(alpha,df=2)
```

#7.4.4

```{r}
pt(c(.8,.9),df=8)
```

#7.4.10
```{r}
mu <- 8622/83
```

#7.4.16
(a)
Find 95% confidence interval for mean.
```{r}
mu <- 1392.6/336
s <- sqrt((336*10518.84 -1392.6^2)/(336*(336-1)))
ci <- qt(0.975,df=335)
mu - ci*(s/sqrt(335))
mu + ci*(s/sqrt(335))
```

(b)
Is the data representative of a normal distribution sample?
```{r}
n <- 336
probs <- c(85,38,35,41,28,24,18,16,16,5,9,21)/n
ggplot(data.frame(y=probs,x=1:length(probs))) + geom_point(mapping=aes(x=x,y=y))
```
No, this data is not representative of a normal distribution sample.


#7.4.18
Use theorem 7.4.2.
Read case study 5.3.1, does data come from normal distribution?
```{r}
data <- c(141,146,144,141,141,136,137,149,141,142,142,147,148,155,150,144,140,140,139,148,143,143,149,140,132,158,149,144,145,146,143,135,147,153,142,142,138,150,145,126,135,142,140,148,146,149,137,140,154,140,149,140,147,137,131,152,150,146,134,137,142,147,158,144,146,148,143,143,132,149,144,152,150,148,143,142,141,154,141,144,142,138,146,145)
y_bar <- mean(data)
mu <- 132.4
n <- length(data)
s <- sqrt((n*sum(data^2)-sum(data)^2)/(n*(n-1)))
(t <- (y_bar-mu)/(s/sqrt(n)))
qt(c(0.025,0.975),df=n-1)
ggplot(data.frame(y=data)) + geom_histogram(aes(y))
```

#7.4.22
```{r}
y_bar <- 4.57
mu <- 0
n <- 317
s <- 18.29
(t <- (y_bar-mu)/(s/sqrt(n)))
qt(0.95,df=n-1)
```

#7.5.2
(a)
```{r}
1-pchisq(8.672,df=17)
```

(b)
```{r}
pchisq(10.645,df=6)
```

(c)
```{r}
pchisq(34.170,df=20)-pchisq(9.591,df=20)
```

(d)
```{r}
pchisq(9.21,df=2)
```

#7.5.4
(a)
$df=1$
```{r}
pchisq(5.009,df=1)
```

(b)
$df=19$
```{r}
df=19
pchisq(30.144,df=df)-pchisq(27.204,df=df)
```

#7.5.6
Random variable of size $n$ from a normal distribution having mean $\mu$ and variance $\sigma^2$. What is the smallest value of $n$ for which the following is true?
$$
P \Big( \frac{S^2}{\sigma^2}<2\Big) \geq 0.95 \\
S^2=\frac{1}{1-n}\Sigma_{i=1}^n (Y_i-\bar{Y})^2 \\
\chi_{n-1}^2 \approx \frac{(n-1)S^2}{\sigma^2} \Rightarrow 
\boxed{
\frac{1}{n-1}\chi_{n-1}^2 \approx \frac{S^2}{\sigma^2}
}
$$

```{r}
n <- c(2:10)
probs <- pchisq(2*(n-1),df=n-1)
ggplot(data.frame(x=n,y=probs)) + geom_point(mapping=aes(x=x,y=y)) + geom_hline(mapping=aes(yintercept=0.95))
```

#7.5.8
```{r}
n <- 19
sigma2 <- 12
alpha <- 0.05
(a <- qchisq(alpha/2,df=n-1)*(12/(n-1)))
(b <- qchisq(1-(alpha/2),df=n-1)*(12/(n-1)))
```




